A North Sámi to South Sámi machine translation prototype

### 2014-02-09 paper/paper.tex
update

>>>>

We evaluate the system for both vocabulary coverage, and translation quality.
For vocabulary coverage, we take two corpora, one in domain (\texttt{schoolbooks}) and 
one general domain.

For translation quality, we selected an text in the domain of school books. The 
text consisted of 300 words. This was then translated by the system and the resulting
translation, and the Norwegian original was given to three translators. They were
 asked to postedit it to make an adequate South Sámi translation, and also to fill
in a feedback questionnaire.
